An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-06-27 EconGrowth.Rnw
Moving back to 100 samples for the CDe resampling.

<<FindError, eval=TRUE>>=
# print(cobbDouglasCountryRow(countryAbbrev="US", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="UK", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="JP", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="CN", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="ZA", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="SA", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="IR", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="TZ", energyType="X"))

cobbDouglasData(countryAbbrev="TZ", energyType="X")

# print(cobbDouglasModel(countryAbbrev="TZ", energyType="X"))
# print(cdeModel(countryAbbrev="TZ", energyType="X"))
# print(cobbDouglasCountryRow(countryAbbrev="ZM", energyType="X"))
@

@@

But, the nearly-complete focus on developed economies closes off 
the possibility of discovering any role that energy plays 
in the development process. In this paper we analyze at least 
two economies in each of the following four categories: 
Developed (technologically advanced with high standards of living), 
BRICS\footnote{Brazil, Russia, India, China, and South Africa} 
(rapid economic growth with standards of living below that of 
developed economies), 
Petrol (petroleum is a substantial source of GDP 
**** Martin: Is this the right way to describe the 
petrol economies? ****); and 
LDCs\footnote{Lesser Developed Countries} 
(living standards near subsistence levels 
**** Martin: Is this the right way to describe the LDC economies? ****). 
(See Table~\ref{tab:Economy_Examples}.)

\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
  \begin{center}
    \begin{tabular}{r c c l l} 
      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
      \hline
      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
      \hline
      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
      \hline
      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
    \end{tabular}
  \end{center}
\end{table}

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
cdeResampleTrianglePlot(energyType="Q")
@

>>>>

@@

But, the near-exclusive focus on developed economies closes off 
the possibility of discovering any role that energy plays 
in the economic development process. In this paper we analyze at least 
two economies in each of the following four categories: 
Developed, 
NICs,\footnote{Newly Industrialized Countries}
OPEC, and 
LDCs.\footnote{Lesser Developed Countries} 
(See Table~\ref{tab:Economy_Examples}.)

\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
  \begin{center}
    \begin{tabular}{r c c l l} 
      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
      \hline
      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
      \hline
      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
      \hline
      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
    \end{tabular}
  \end{center}
\end{table}

@@

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
cdeResampleTrianglePlot(energyType="Q")
@
